Data analysis to support temporary cycleways

### 2020-05-13 README.Rmd
Update build code

```{r, eval=FALSE}
params = list(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
  )

old_wd = setwd("cities")
rmarkdown::render("leeds.Rmd") # check
rmarkdown_files = paste0(tolower(las_top$name), ".Rmd")
lapply(rmarkdown_files, rmarkdown::render, params = params)
setwd(old_wd)
webshot::install_phantomjs()
# general analysis of data
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
readr::write_csv(rtid, "rtid.csv")
piggyback::pb_upload("rtid.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
    (lanespsvbackward + lanesbackward) > 1,
  !grepl(pattern = "motorway", highway)
)
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

@@

```{r, engine='zsh', eval=FALSE}
# deploy
git clone git@github.com:cyipt/popupCycleways
cd popupCycleways
git checkout gh-pages
# git rm -rf .
# git commit --allow-empty -m 'Initial gh-pages commit'
# git push origin gh-pages
# git checkout master
# cp -Rv ../README* . # it's 100 MB!
git status
cp -Rv ../cities/*.html . # it's 100 MB!
git status
ls -hal
pandoc -o index.html ../README.md
firefox index.html
git status
git commit -am 'Update results'
git push origin gh-pages
cd ..
```

>>>>

```{r, eval=FALSE}
old_wd = setwd("cities")
rmarkdown::render("sheffield.Rmd") # check
rmarkdown_files = paste0(tolower(las_top$name), ".Rmd")
for(i in rmarkdown_files) {
  rmarkdown::render(i)
}
# lapply(rmarkdown_files, rmarkdown::render)
# parallel::mclapply(rmarkdown_files, rmarkdown::render, mc.cores = 5)
getwd()
browseURL("liverpool.html")
setwd(old_wd)

webshot::install_phantomjs()
# general analysis of data
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
readr::write_csv(rtid, "rtid.csv")
piggyback::pb_upload("rtid.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
    (lanespsvbackward + lanesbackward) > 1,
  !grepl(pattern = "motorway", highway)
)
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

@@

```{r, engine='zsh', eval=FALSE}
# deploy
git clone git@github.com:cyipt/popupCycleways
cd popupCycleways
git checkout gh-pages
# git rm -rf .
# git commit --allow-empty -m 'Initial gh-pages commit'
# git push origin gh-pages
# git checkout master
# cp -Rv ../README* . # it's 100 MB!
git status
cp -Rv ../cities/*.html . # it's 100 MB!
git status
ls -hal
# firefox index.html
git status
git commit -am 'Update results'
git push origin gh-pages
cd ..
```

### 2020-05-13 cities/bristol.Rmd
Update build code

```{r Bristol}
setwd("..")
region_name = "Bristol"
source("code/build.R")
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

>>>>

```{r Bristol}
setwd("..")
region_name = "Bristol"
source("code/build.R", local = TRUE)
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

### 2020-05-13 cities/leeds.Rmd
Update build code

```{r leeds}
setwd("..")
region_name = "Leeds"
source("code/build.R")
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

>>>>

```{r leeds}
setwd("..")
region_name = "Leeds"
source("code/build.R", local = TRUE)
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

### 2020-05-13 cities/leicester.Rmd
Update build code

```{r Leicester}
setwd("..")
region_name = "Leicester"
source("code/build.R")
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

>>>>

```{r Leicester}
setwd("..")
region_name = "Leicester"
source("code/build.R", local = TRUE)
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

### 2020-05-13 cities/liverpool.Rmd
Update build code

```{r Liverpool}
setwd("..")
region_name = "Liverpool"
source("code/build.R")
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

>>>>

```{r Liverpool}
setwd("..")
region_name = "Liverpool"
source("code/build.R", local = TRUE)
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

### 2020-05-13 cities/manchester.Rmd
Update build code

```{r Manchester}
setwd("..")
region_name = "Manchester"
source("code/build.R")
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```

>>>>

```{r Manchester}
setwd("..")
region_name = "Manchester"
source("code/build.R", local = TRUE)
m
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods developed for the project.", digits = 0)
```
